\documentclass[a4paper]{article}

\input{doc/version}

\usepackage{enumitem}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{listings}
\usepackage{natbib}

\renewcommand{\ttdefault}{pcr}

\begin{document}

\begin{titlepage}
\begin{center}

\Huge{libsupermesh Version \version~ Manual} \\[0.15\textheight]
\Large{Dr. Patrick E. Farrell, Dr. J. R. Maddison, \\ Mr. I. Panourgias}

\end{center}
\end{titlepage}

\tableofcontents

\section{Introduction}

libsupermesh is a library for serial and parallel mesh intersection, or
supermeshing \citep{farrell2009,farrell2009a}. libsupermesh specifically
includes components used in the local supermeshing approach described in
\citet{farrell2011}. Here, given two input finite element meshes, elements in
each mesh which intersect are identified, and a local mesh of their intersection
is generated.

\section{Building libsupermesh}

libsupermesh is built using CMake\footnote{\url{https://cmake.org/}}, for
example via:
\begin{lstlisting}[language = sh, frame = single]
cd [LIBSUPERMESH_SOURCE_PATH]/build
cmake [LIBSUPERMESH_SOURCE_PATH] \
  -DCMAKE_INSTALL_PREFIX=[LIBSUPERMESH_INSTALL_PATH]
make
make install
\end{lstlisting}
where \verb+[LIBSUPERMESH_SOURCE_PATH]+ is the path to the source directory, and
\verb+[LIBSUPERMESH_INSTALL_PATH]+ is the path to the installation directory.
Note that libsupermesh cannot be built in the source directory.

\subsection*{CMake variables}

\begin{description}[font=\ttfamily\bfseries]
  \item[CMAKE\_BUILD\_TYPE] Build type. Valid options are ``Release'' and
    ``Debug''. Default ``Release''.
  \item[BUILD\_SHARED\_LIBS] Build a shared library. Default disabled. 
  \item[LIBSUPERMESH\_AUTO\_COMPILER\_FLAGS] Choose compiler flags
    automatically, enabling aggressive optimisation options for the Release
    build and additional debugging options for the Debug build. Active only if
    the GNU or Cray compilers are used. This overrides other CMake compiler flag
    variables. Default enabled.
  \item[LIBSUPERMESH\_ENABLE\_JUDY] Use the Judy library. Requires an available
    installation of Judy. Default disabled.
  \item[LIBSUPERMESH\_ENABLE\_TIMERS] Enable internal timers for parallel
    supermeshing. Default disabled.
  \item[LIBSUPERMESH\_OVERLAP\_COMPUTE\_COMMS] Overlaps communication and some
    calculation in parallel supermeshing. Default disabled.
\end{description}

\subsection*{Build targets}

\begin{description}[font=\ttfamily\bfseries]
  \item[make] Default build. Builds the library and unit tests.
  \item[make test] Runs the unit tests.
  \item[make doc] Builds this manual.
\end{description}

\bibliography{doc/bibliography}
\bibliographystyle{plainnat}

\end{document}
